\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-01-28 tex/paper.tex
Added load testing text

\subsection{Access rights}
\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } p \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\subsubsubsection{API}
\label{sec:API}
In this work a RESTful API was implemented and used for back-end $\Iff$ front-end
communication.

@@

\subsubsection{REST Endpoints}
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:

@@

\subsection{Findings}
\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enourmous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak (\fix relate to 
graph) for what Casbah can handle on a single server.

@@

\subsubsection{Security of the system}
\paragraph{Authorization}
The authorization of the system is currently being handled by LDAP

>>>>

\subsection{Access rights}
The \textit{a} notation is meant to symbolise an access token, and if \textit{a} exists in the requested enitity of
the matrix the corresponding user to that entity has full access to the corresponding object.

\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } p \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\subsubsection{API}
\label{sec:API}
In this work a RESTful API was implemented and used for back-end $\Iff$ front-end
communication.

@@

\subsubsubsection{REST Endpoints}
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:

@@

\subsection{Findings}
\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak (\fix relate to 
graph) for what Casbah can handle on a single server.

\subsubsubsection{Load Testing}
Wrk was used to load test the back-end. It is a multi-threaded benchmarking tool for HTTP which can
create large loads. The testing was done locally on a virtual server having 6 CPU cores and 48GB of
RAM. The results that will be analysed are latency and load of the server as that will give a fair
judgement of how well the system can perform on any given machine.

\textbf{GET requests}
To be able to determine what is the bottleneck of the back-end three different types of \textit{GET
requests} are performed. The first one tries to maximise the number of requests that spray-can (HTTP
server) can handle with the given specifications and therefore the server just returns 200 (OK). The
second request requests the simplest API call which involves getting all currently stored projects
from the MongoDB instance. As this involves the server answering with some payload, the third
request is simply the same amount of static payload as the second request but without involving any
connections to MongoDB.

\textbf{POST requests}

@@

\subsubsection{Security of the system}
\paragraph{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius is mainly
focussed at being deployed in internal networks which usually has an LDAP service enabled. LDAP also
makes it easier for the user to login as no separate account is needed for Perius and thus the user
can use the same account as for all the LDAP connected services on the internal network.
